Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-07-03 paper/paper.tex
small tweaks; work in progress

\begin{lstlisting}
  val new_cont: Cont = { case (config@Config(ae, env_, store, time), seen, m) =>
    val new_time = config.tick
    val baddr = allocBind(x, new_time);  val new_env = env + (x -> baddr)
    val new_store = store.update(baddr, atomicEval(ae, env_, store))
    aeval(Config(e, new_env, new_store, new_time), seen, continue, m)
  }
\end{lstlisting}

>>>>

\begin{lstlisting}
  val new_cont: Cont = { case (config @ Config(ae, env_, store, time), seen, m) =>
    val new_time = config.tick
    val baddr = allocBind(x, new_time);  val new_env = env + (x -> baddr)
    val new_store = store.update(baddr, atomicEval(ae, env_, store))
    aeval(Config(e, new_env, new_store, new_time), seen, continue, m)
  }
\end{lstlisting}
